\LARGE \bf Approximately Orchestrated Road Traffic Automata:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
crazy intersection example added

\usepackage[pdftex]{graphicx}
% TODO remember we need to meet color compliance:
% http://its.papercept.net/conferences/support/general.php

@@

The map also has a geometric interpretation, used for visualization and
measuring physical distances. A road contains a sequence of points, defining
the center line that divides the road into two directions of travel. AORTA
interprets these points as straight lines and projects parallel lanes out using
a fixed width. Turns are modeled with a single straight line connecting the end
of one lane to the start of another. \commentc{Illustrate through a figure?}
\commentd{maybe a subfloat by the turn conflicts, sure}

@@

Intersections check for collisions by examining the turn each agent is
performing and verifying that no other agent is simultaneously performing a
conflicting turn. AORTA has a low-granularity model of turn conflict. If two
vehicles at any point along two different turns could ever come into contact,
then the turns are always in conflict, no matter where the agents actually are
along that turn. This is visualized in figure \ref{fig:conflicts}. Further work
is required before higher granularity can be introduced through space-time
tiling intersections \cite{JAIR08-dresner}, due to some of the complex
intersection geometries inferred from OSM \commentpk{If there is an image for
one such complex intersection geometry, we can place it next to the current fig
3 using a subfloat}.

@@

\begin{figure}[h]
  \centering \includegraphics[scale=0.5]{turn_conflicts.png}
  \caption{An agent cannot turn left while agents on the perpendicular road cross}
  \label{fig:conflicts}
  \vspace{-15pt}
\end{figure}

>>>>

\usepackage[pdftex]{graphicx}
\usepackage{subfig}
% TODO remember we need to meet color compliance:
% http://its.papercept.net/conferences/support/general.php

@@

The map also has a geometric interpretation, used for visualization and
measuring physical distances. A road contains a sequence of points, defining
the center line that divides the road into two directions of travel. AORTA
interprets these points as straight lines and projects parallel lanes out using
a fixed width. Turns are modeled with a single straight line connecting the end
of one lane to the start of another.

@@

Intersections check for collisions by examining the turn each agent is
performing and verifying that no other agent is simultaneously performing a
conflicting turn. AORTA has a low-granularity model of turn conflict. If two
vehicles at any point along two different turns could ever come into contact,
then the turns are always in conflict, no matter where the agents actually are
along that turn. This is visualized in figure \ref{fig:conflicts}. Further work
is required before higher granularity can be introduced through space-time
tiling intersections \cite{JAIR08-dresner}, due to some of the complex
intersection geometries inferred from OSM. An example of such a difficult
intersection is shown in figure \ref{fig:crazyIntersection}.

@@

\begin{figure}[h]
  \centering
  \subfloat[An agent cannot turn left while agents on the perpendicular road
  cross]{
    \includegraphics[scale=0.4]{turn_conflicts.png}
    \label{fig:conflicts}
  }
  ~ % horizontal spacing, mostly for the sake of the captions
  \subfloat[A difficult intersection to tile in New Orleans, Louisiana. Note
  there are no overpasses pictured.]{
    \includegraphics[scale=0.4]{crazy_intersection.png}
    \label{fig:crazyIntersection}
  }
  \caption{Examples of AORTA's modeling of intersections and turns}
  \vspace{-15pt}
\end{figure}
